Accurate relative location using coda waves of a poorly recorded cluster of earthquakes near Kalannie, Western Australia

### 2012-07-24 paper3/paper3.tex
Creating a git version of paper3 to start working on

\documentclass[draft,jgrga]{agutex}
\bibliographystyle{agufull08}
%\usepackage{rotating}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% optional article formats author might want to use

@@

%  Figures and Tables should be placed at the end of the article,
%  after the references.
%
%  Uncomment the following command to include .eps files
%  (comment out this line for draft format):
  \usepackage[dvips]{graphicx}
%
%    Uncomment the following command to allow illustrations to print
%    when using Draft:
  \setkeys{Gin}{draft=false}
%
% Substitute one of the following for [dvips] above
% if you are using a different driver program and want to
% proof your illustrations on your machine:
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
% See how to enter figures and tables at the end of the article, after
% references.
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

@@

% Shorter version of title entered in capital letters:
\titlerunninghead{EARTHQUAKE LOCATION USING CODA WAVES}

@@

\authoraddr{J. Hauser,
NORSAR, Postboks 53, Instituttveien 25, N-2027 Kjeller, Norge}

@@

\title{Relocating a cluster of earthquakes using coda waves from a single station}
%
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
% You may use \\ to break the title over several lines.

@@

\authors{D. J. ROBINSON, \altaffilmark{1,} \altaffilmark{2}
M. SAMBRIDGE,  \altaffilmark{1}
R. SNIEDER \altaffilmark{3}
and J. HAUSER \altaffilmark{1,} \altaffilmark{4}}
%E. Mosley-Thompson, \altaffilmark{2} R. Williams, \altaffilmark{3}
%and J. R. McConnell\altaffilmark{4}}

@@

\altaffiltext{4}{Earthquakes and the Environment Program, NORSAR}

@@

\section{Introduction}
\begin{itemize}
\item Brief discussion of existing earthquake location techniques - first arrivals - need for good station coverage etc.
\item Non-technical overview of CWI (\citealp{dr_Snieder05a}; \citealp{dr_Snieder06a})
\item Comment how CWI pairwise separation does not require azimuthal station coverage \citep{dr_Robinson07b}
\item Mention probabilistic version for CWI based separation (ref \textbf{paper1})
\end{itemize}

\section{Theory}
\begin{itemize}
\item Key CWI formulae from \citet{dr_Snieder05a},
\citet{dr_Snieder06a} and \textbf{paper1}
\item Formulation of the misfit function $L$ (i.e. extract from Thesis Chapter 5)
\item Discuss minimization of $L$ using Polak-Ribiere conjugate gradient method
\item Derivation of Derivatives
\end{itemize}

\section{Benchmarking}
\begin{itemize}
\item Introduce 2D synthetic studies (relocating 50 earthquakes) and show results for cases with
two different uncertainty levels (Figures \ref{fig-2D50eq-relocation_eg1} and
\ref{fig-2D50eq-relocation_eg3})
\item Explain CWI constraints in terms of a network of points
\item Repeat the relocations with reduced pairwise linkage and show results
(Figure \ref{fig:optimisationresults-2Dsynth})
\item Discuss process of repeating optimisation with 25 randomly chosen starting locations
 and compare results to the best optimisation chain - i.e. stability of the inversion.
\item \textbf{Malcolm and Roel - at this stage I am not planning to include detailed pictures of the 2D
inversions and discuss rotational error structure. I don't think it is needed in this paper but I welcome your thoughts}
\item Repeat the experiment in 3D and show results
(Figure \ref{fig:optimisationresults-3Dsynth})
\item Discuss differences between the 2D and 3D versions -i.e. failed convergence (in 3D) versus slow convergence (in 2D)
\end{itemize}

\section{Relocating Earthquakes on the Calaveras Fault}
\begin{itemize}
\item Introduce the Calaveras Fault and provide a brief background of why it is chosen here (Figure \ref{fig:-eqopti-California-Calaveras})
\item Discuss Catalogue Locations - hypoDD locations and CWI locations
(Figure \ref{fig-69Calaverasevents_eg1})
\begin{itemize}
\item mention difference between hypoDD inversions when 68 or
308 earthquakes considered but don't show figure (i.e. difference in coordinates for
the two solutions is roughly 2\,m)
\item provide details on CWI application - waveform selection, filtering etc.
\end{itemize}
\item Discuss comparison between CWI and catalogue locations - first order performance of CWI and clustering
\item Discuss comparison between CWI and hypoDD locations - second order result and streaks.
\end{itemize}

\section{Dependance on the number of stations}

\begin{itemize}
\item Explain issues associated with poor station coverage - superimpose
the three SWSZ (i.e. Australian) stations onto  Figure
\ref{fig:-eqopti-California-Calaveras}
\item Show setup for consideration of fewer stations (Table
\ref{tab:Calaveras-stationremoval}
and Figure \ref{fig:-eqopti-Calaveras-substations})
\item Show the results (Figures \ref{fig-68Calaveras_CWIxyloc-statremove}
to \ref{fig-68Calaveras_hypoDDyzloc-statremove} and Figure \ref{fig-statremoval_summarystats})
\item Discuss the better performance of CWI with fewer stations
\item Question/Discuss why hypoDD continues to suggest streaks with 2 or 3 stations - there must be regularization
\end{itemize}

\section{Combining travel time and CWI constraints}

\begin{itemize}
\item Pose the problem
\item Introduce the idea of a travel time based separation PDF with mean event locations from hypoDD outputs and
some measure of uncertainty (we will consider three levels of uncertainty as in paper1).
\item Explain how to combine the CWI based posterior with these new travel time based separation PDFs
\item Show the derivatives of the travel time based separation PDF
\item Undertake the combined inversion show/discuss findings (Figure \ref{fig-68Calaverasevents_ttandcoda1} )
\end{itemize}

\section{Combining CWI and travel times when the travel times constrain a limited number of events}

\begin{itemize}
\item Explain the idea of a temporary deployment of stations i.e. for aftershocks
\item Discuss Omori formula and the $M_s$7.8 Hokkaido-Nansei-Oki earthquake
(Figure \ref{fig:Omorifigure}; \citealp{dr_Utsu95a})
\item Show/Discuss results (Figure \ref{fig-68Calaverasevents_ttsubsetandcoda1})
\end{itemize}

\section{Conclusions}
\begin{itemize}
\item Emphasise strengths of the CWI relocation (i.e. with small number of stations,
linking temporary deployments with catalogue locations)
\item Discuss potential applications e.g. intraplate/downhole/tunnel monitoring etc.
\end{itemize}

@@

%% ------------------------------------------------------------------------ %%
%
%  REFERENCE LIST AND TEXT CITATIONS
%
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% Or,
%
% If you use BiBTeX for your References, please produce your .bbl
% file and copy the contents into your paper here.
%
% Follow these steps:
% 1. Run LaTeX on your LaTeX file.
%
% 2. Run BiBTeX on your LaTeX file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
% 4. Comment out the old \bibliographystyle and \bibliography commands.
%
% 5. Run LaTeX on your new file before submitting.
%
% AGU does not want a .bib or a .bbl file, but asks that you
% copy in the contents of your .bbl file here.
\bibliography{../../refs/drrefs}
% DR ... \begin{thebibliography}{}

@@

% DR ... \end{thebibliography}

@@

%%% End the article here:
% Put the figures here....
\clearpage
\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/locs_2D_50eq_1.eps}
\caption{Example 1 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise $\bar{\sigma}_N=0.02$.
Actual and optimisation event locations
are shown in blue and red circles, respectively.}
\label{fig-2D50eq-relocation_eg1}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/locs_2D_50eq_3.eps}
\caption{Example 3 - Synthetic relocation of 50 earthquakes in 2D using all constraints with noise
$\bar{\sigma}_N= 2 \sigma_{1to5Hz}(\delta_t)$.
 Actual and optimisation event locations
are shown in blue and red circles, respectively.}
\label{fig-2D50eq-relocation_eg3}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth2Dmulti/ressummary_2Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 2D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The bottom subplot shows the average minimum number of branches required to link the 2450 pairs.}
 \label{fig:optimisationresults-2Dsynth}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_optimisation/synth3Dmulti/ressummary_3Dsynth50eq.eps}
\caption{Statistical measures of error in the optimisation solutions for the 3D synthetic cases when all (blue)
and best (red) results are considered. The statistics $\Delta_{max}$, $\Delta_\mu$ and
$\Delta_\sigma$ are the maximum, mean and standard deviation of the coordinate error, respectively.
The absence of the blue and red lines below 60\% and 30\% indicates a breakdown in the solutions
when all or best optimisation result(s) are considered, respectively.}
\label{fig:optimisationresults-3Dsynth}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/gmt_california/CaliforniaCalaverasMap1.eps}
\caption{Elevation in California showing location
of the 308 event Calaveras cluster (black star) and 805 seismic stations (red triangles).}
\label{fig:-eqopti-California-Calaveras}
\end{figure}

\begin{figure}
\includegraphics{diags/CalaverasLoc1.eps}
\caption{Comparison of earthquake hypocenters using three different methods: catalogue location (column 1), hypoDD with all
308 events (column 2) and CWI example 1 (column 3).
Note that in the case of the CWI locations we consider only the 68 earthquakes in red, the
blue events are shown for the purpose of orientation only.}
\label{fig-69Calaverasevents_eg1}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasMap/matlab/Calaveras_substationmap}
\caption{Location of the 10 stations (red triangles) used to relocate the Calaveras events.
Stations are removed one at a time according to the order in Table \ref{tab:Calaveras-stationremoval} and the events
relocated (see Figures \ref{fig-68Calaveras_CWIxyloc-statremove} to \ref{fig-68Calaveras_hypoDDyzloc-statremove}).
The 304 Calaveras events are indicated with black circles.}
\label{fig:-eqopti-Calaveras-substations}
\end{figure}

\begin{figure}
\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc2.eps}
\caption{....}
\label{fig-CWIreducesstats}
\end{figure}

\begin{figure}
\includegraphics[angle=90,height = 50pc]{diags/CalaverasLoc3.eps}
\caption{....}
\label{fig-HYPODDreducesstats}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/CalaverasLoc4.eps}
\caption{Statistics on coordinate differences for reduced station inversions. Differences
are computed between the inversion results (CWI and hypoDD) and the complete hypoDD
locations for all 308 events. The top subplot illustrates the number of constrainable
events in the CWI and hypoDD inversions as a function of the stations considered.}
\label{fig-statremoval_summarystats}
\end{figure}

\begin{figure}
\noindent\includegraphics{diags/CalaverasLoc5.eps}
\caption{Locations of the 68 Calaveras earthquakes combining all available coda wave and travel time constraints with three different
levels of uncertainty on the travel time PDFs. Column 1 sets $\sigma_x = \sigma_y = 19.5$\,m and $\sigma_z = 15$\,m
(after \citealp{dr_Waldhauser08a}), Column 2 uses $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m and
column 3 considers $\sigma_x = \sigma_y = 152$\,m and $\sigma_z = 232$\,m (after \citealp{dr_Shearer97a}). }
\label{fig-68Calaverasevents_ttandcoda1}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{diags/OmoriFigure.eps}
\caption{Cumulative number of aftershocks for the Hokkaido-Nansei-Oki, Japan
$M_s=7.8$ earthquake of 12 July 1993 according to the best fitting modified Omori Formula
\citep{dr_Utsu95a}. The leftmost dashed, middle solid and rightmost dashed signify aftershocks occurring before, during and
after the deployment of a temporary array installed 7 days after the main shock and left for
65 days.}
\label{fig:Omorifigure}
\end{figure}

\begin{figure}
\noindent\includegraphics{diags/CalaverasLoc6.eps}
\caption{Left - Combined travel time and coda wave inversions using travel time constraints on
22 (or 32\%) of the events and coda waves from station CCO only. All travel time based uncertainties
are assigned $\sigma_x = \sigma_y = 3 \times19.5$\,m and $\sigma_z = 3\times15$\,m. Right - travel time
relocation only (i.e. no CWI) using ........}
\label{fig-68Calaverasevents_ttsubsetandcoda1}
\end{figure}

\clearpage
\begin{table}
\caption{Stations considered when exploring the effect of reduced station coverage.}
\label{tab:Calaveras-stationremoval}
\begin{tabular}{|r|l|}
\hline
Number of & Station Names\\
Stations  & \\
\hline
10 & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL, JRR\\
9  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD, JHL\\
8  & CCO, JCB, JST, CMH, HSP, JAL, CSC, JST, CAD\\
7  & CCO, JCB, JST, CMH, HSP, JAL, CSC \\
6  & CCO, JCB, JST, CMH, HSP, JAL \\
5  & CCO, JCB, JST, CMH, HSP \\
4  & CCO, JCB, JST, CMH \\
3  & CCO, JCB, JST \\
2  & CCO, JCB \\
1  & CCO \\
\hline
\end{tabular}
\end{table}

>>>>

%\documentclass[draft,grl]{agutex}
\documentclass[grl]{agutex}
\bibliographystyle{agufull08}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% optional article formats author might want to use

@@

%  Figures and Tables should be placed at the end of the article,
%  after the references.
%
%  Uncomment the following command to include .eps files
%  (comment out this line for draft format):
\usepackage{graphicx}
\usepackage{multirow}  % DR Needed to setup figure 1 - must comment out for final version..
%
%    Uncomment the following command to allow illustrations to print
%    when using Draft:
\setkeys{Gin}{draft=false}
%
% Substitute one of the following for [dvips] above
% if you are using a different driver program and want to
% proof your illustrations on your machine:
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
% See how to enter figures and tables at the end of the article, after
% references.
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

@@

% Shorter version of title entered in capital letters:
\titlerunninghead{LOCATING POORLY RECORDED EARTHQUAKES USING CODA WAVES}

@@

\authoraddr{P. Cummins,
Research School of Earth Sciences, Australian National University, Canberra, ACT, 0200, Australia.
 (phil.cummins@anu.edu.au) and
Risk Research Group, Geoscience Australia, GPO Box 378, Canberra, ACT, 2601, Australia.
 (phil.cummins@ga.gov.au)}

\authoraddr{J. Dawson,
Earth Monitoring Group,Geoscience Australia, GPO Box 378, Canberra, ACT, 2601, Australia.
 (john.dawson@ga.gov.au)}

@@

\title{Accurate relative location using coda waves of a poorly recorded cluster of earthquakes near Kalannie, Western Australia}
%
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
% You may use \\ to break the title over several lines.

@@

\authors{D. J. ROBINSON, \altaffilmark{1,} \altaffilmark{2}
M. SAMBRIDGE,  \altaffilmark{1}
R. SNIEDER, \altaffilmark{3}
P. CUMMINS \altaffilmark{1,} \altaffilmark{2}
AND J. DAWSON \altaffilmark{4}}
%E. Mosley-Thompson, \altaffilmark{2} R. Williams, \altaffilmark{3}
%and J. R. McConnell\altaffilmark{4}}

@@

\altaffiltext{4}{Earth Monitoring Group, Geoscience Australia}

@@

\section{Introduction}
\begin{itemize}
\item South West Seismic Zone (SWSZ) - one of Australia's most active source zones
\item Poor station coverage makes accurate location difficult
\item Kalannie earthquake cluster (figure \ref{fig:-Kalannie-map}(a))
\item \citet{dr_Dawson08a} composite mechanism (ref table \ref{tab-Dawson-Kalannie-results})
\item Validity of composite mechanism assumes overlapping rupture on the same fault - we demonstrate that
assumption holds despite the poor station coverage
\end{itemize}

\section{Methodology}
\begin{itemize}
\item Compute Kalannie event sizes (Table \ref{tab:Kalannie-eventsizes}) and comment on location
accuracy required to demonstrate that events are overlapping
\item Relative location with a few stations - use the coda
\item CWI separation (\citealp{dr_Snieder05a}; \citealp{dr_Snieder06a})
\item Possible to get separation estimate with a single station (e.g. \citealp{dr_Robinson07b})
\item \textbf{ref Paper1} - formulates CWI probabilistically for a pair of events - must comment on wavelength normalisation
\item \textbf{ref Paper2} - formulation of the joint posterior, misfit function $L$ and minimization by optimisation.
\item Problem with optimisation approach is that it gives a single solution only and can get trapped in
local minima. We use Markov-Chain Monte-Carlo (MCMC) here which allows a complete assessment of uncertainty.
This is only possible because of the small number of events considered.
\item \textbf{Malcolm and Roel - there is potentially a large number of equations to show here. I propose that we keep
the number of equations as small as possible and refer readers to the other papers and the thesis for details. Any
thoughts?}
\end{itemize}

\section{Results}

\begin{itemize}
\item Discuss waveforms, first arrival similarity and filtering between 1 and 2\,Hz (Figure \ref{fig:-Kalannie-map}(b))
\item We only have access to data from 3 stations MORW, BLDU and KLBR (Figure \ref{fig:-Kalannie-map}(a))
\item Application of CWI on event pairs (Figure \ref{fig:-Kalannie-map}(b))
\item Computation of CWI based pairwise separation posteriors (Figure \ref{fig:Kalannie-CWI-Posteriors})
\item Compare MCMC results (Expected Value and standard error) to optimisation solution (Table \ref{tab:Kalannie-InversionRes})
\item MCMC in more detail: 1D marginals, covariance and correlation (Figure \ref{fig:Kalannie-CWI-NAB-1Dmarginals})
\item MCMC in more detail: example 2D marginal (Figure \ref{fig:Kalannie-2Dmarginals_param23}).
Shows that events 1 and 2 are close but not co-located.
\item Discuss the separation estimates which incorporate CWI from all pairs (e.g. Table \ref{tab:-KalannieRes-separations})
\end{itemize}

\section{Conclusions}
\begin{itemize}
\item The power of CWI when limited stations available
\item Advantage of the MCMC inversion approach (i.e. detailed picture of uncertainty). Disadvantage that it
is computationally expensive (ref \textbf{Paper2} for optimisation approach with more events).
\item Demonstration that the events are close but not co-located. Consistent with hypothesis that the
four ruptures overlap on the same fault.
\end{itemize}

@@

% Put the figures here....

%% ------------------------------------------------------------------------ %%
%
%  REFERENCE LIST AND TEXT CITATIONS
%
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% Or,
%
% If you use BiBTeX for your References, please produce your .bbl
% file and copy the contents into your paper here.
%
% Follow these steps:
% 1. Run LaTeX on your LaTeX file.
%
% 2. Run BiBTeX on your LaTeX file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
% 4. Comment out the old \bibliographystyle and \bibliography commands.
%
% 5. Run LaTeX on your new file before submitting.
%
% AGU does not want a .bib or a .bbl file, but asks that you
% copy in the contents of your .bbl file here.

\bibliography{../../refs/drrefs}
% DR ... \begin{thebibliography}{}

@@

% DR ...\end{thebibliography}

@@

%%% End the article here:
\clearpage
\begin{figure}
\begin{tabular}{ll}
(a) & (b) \\
\multirow{15}{*}{\includegraphics[width = 16pc]{../../thesis_version2/diags/eq_location_simple/KalannieMap/KalannieMap1.eps}} &
\multirow{15}{*}{\includegraphics[width = 20pc]{diags/waves_and_CWIest.eps}} \\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{tabular}
\caption{(a) Map of the South West Seismic Zone (SWSZ) illustrating the location of the Kalannie earthquake cluster,
the \cite{dr_Dawson08a} composite focal mechanism for the Kalannie events,
large historical events (focal mechanisms), observed seismicity between 1998 to 2007 (circles) and
Quaternary fault scarps (black lines) identified by \citet{dr_Clark09a}. The three available recording stations
MORW (162\,km), BLDU (67\,km) and KLBR (169\,km) are depicted with red triangles. Figure courtesy of
\citet{dr_Dawson08a} with minor modifications. (b) Example waveforms and CWI separation estimates
for the Kalannie events. The top row illustrates waveforms at station MORW for Event 1 normalised to maximum
amplitude and filtered between 1 and 2\,Hz for the three channels N,Z,E. Relative P, S and surface wave arrivals are also
indicated at 0, 19 and 27\,s, respectively. Middle row demonstrates similarity of first arrivals at station MORW for Events 1 and 2 in
the three channels. The bottom row shows the CWI separation estimates at MORW
as a function of sliding time window with width 5\,s for event pair 1 and 2. The three traces
represent different channels and the vertical black lines
enclose the region between $t=$5\,s and $t_{surf}$ that we consider for the remaining analysis.}
\label{fig:-Kalannie-map}
\end{figure}

\begin{figure}
\noindent\includegraphics[width = 20pc]{../../thesis_version2/diags/eq_location_simple/Kalannie_figs/Kalannie_Posteriors_timeclip_1to2Hz_tw5.eps}
\caption{Posterior functions $P_{ij}(\widetilde{\delta}_{t}|\widetilde{\delta}_{CWIN})$ for the Kalannie
event pairs $i$ and $j$. A
second $x$-axis is shown in separation units of meters for convenience.}
\label{fig:Kalannie-CWI-Posteriors}
\end{figure}

\begin{figure}
\begin{tabular}{ll}
(a) & (b) \\
\multirow{3}{*}{\noindent\includegraphics[width = 25pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie-CWI-NAB-1Dmarginals-withareas.eps}} & \multirow{2}{*}{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_covariance.eps}}\\
&  \\
 & \\
 &
 \\
\\
\\
\\
\\
& (c) \\
&  \multirow{2}{*}{\includegraphics[width = 10pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_correlation.eps}}\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\\
\end{tabular}
\caption{(a) One dimensional marginals for each of the six unknown Kalannie earthquake coordinates.
Labels $\hat{x}$, $\hat{y}$ and $\hat{z}$ refer to a local coordinate system with
origin corresponding to the event 1 location. Subscripts indicate the event number. Missing
parameters $\hat{y}_2$, $\hat{z}_2$ and $\hat{z}_3$ are set to 0 to remove rotational non-uniqueness without
loss of generality. Grey shaded regions illustrate the probability of each coordinate
being within 500\,m of the origin. The relative size of the shaded area
indicates that all event coordinates are likely within 500\,m of event 1
(see table \ref{tab:Kalannie-InversionRes} for actual areas). (b) Covariance and (c) correlation matrices
for the Kalannie earthquake location coordinates.
Different colours in the covariance matrix suggest different levels of resolvability between
coordinates. The off-diagonal structure of the correlation matrix indicates
a low level of trade-off between different coordinates.}
\label{fig:Kalannie-CWI-NAB-1Dmarginals}
\end{figure}

\begin{figure}
\noindent\includegraphics[width=20pc]{../../thesis_version2/diags/eq_location_simple/KalannieNAB/Kalannie_marginals2Dcont_param2_3.eps} \\
\caption{Marginal $P(\mathbf{e}_3) = P(\hat{x}_3,\hat{y}_3)$  for the location of event 3 normalised to unit volume.
We observe a clear maximum
near ($\hat{x}_3=290$\,m, $\hat{y}_3=300$\,m) and a local minimum near the origin. The black lines
enclose the 68\% confidence region. This figure suggests that events 3 and 1 (at origin) are close to one another but
not co-located and is consistent with the inversion results from the optimiser (magenta circle) and
MCMC (green circle).}
\label{fig:Kalannie-2Dmarginals_param23}
\end{figure}

\clearpage

\begin{table*}
\caption[InSAR source parameters for composite Kalannie mechanism]
{\cite{dr_Dawson08a} InSAR derived source parameters for a composite Kalannie mechanism with 1$\sigma$ uncertainties.
These parameters represent the point source which best explains the observed deformation at the surface. }
\label{tab-Dawson-Kalannie-results}
\begin{tabular}{ccccccc}
\hline
Long. ($^o$) & Lat. ($^o$) & Depth (km) & Mag. ($M_w$) & Strike ($^o$) & Dip ($^o$) & Rake ($^o$) \\
\hline
117.1700 & -30.1484 & 1.15 & 4.39 & 231.1 & 51.9 & 132.6 \\
$\pm$0.12\,km &  $\pm$0.10\,km & $\pm$0.08 & $\pm$0.06 & $\pm$12.1 & $\pm$6.2 & $\pm$11.1 \\
\hline
\end{tabular}
\end{table*}

\begin{table}
\caption[Kalannie earthquake magnitudes, seismic moments and dimensions]
{Estimated seismic moment $M_o$, moment magnitude $M_w$ and rupture diameter $2a$ for the
four Kalannie events using the local magnitude $M_L$ of the Geoscience Australia catalogue and conversion
formula discussed in text. In the case of the composite event (comp) we use the $M_w$ of \citet{dr_Dawson08a} and reverse
the calculations.}
\label{tab:Kalannie-eventsizes}
\begin{tabular}{c|ccccc}
\hline
Event & Date     & $M_L$ & $M_o$           & $M_w$   &  $2a$\\
      & (2005)   &       & ($10^{14}$\,Nm) &         &  (m)\\
\hline
1     &  21-Sept & 4     & $9.55$          & 3.9     & 694\\
2     &  21-Sept & 3.7   & $4.29$          & 3.7     & 531\\
3     &  22-Sept  & 4.1  & $12.47$         & 4       & 759\\
4     &  22-Sept  & 3.9  & $7.31$          & 3.8     & 635\\
comp  &  NA       & 4.6  & $48.4$          & 4.39    & 1192\\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{Inversion results for the Kalannie earthquake coordinates. The expected value $E[\bar{X}_i]$
and $var(\bar{X}_i)$ (the standard error of $E[\bar{X}_i]$) come from the Markov-chain Monte-Carlo approach, whereas
$\hat{x}_i^*$ result from the optimiser. The
outputs of both inversion procedures are consistent within the bounds of the standard error.
In the final column we show the probability of each event coordinate being within 500\,m of the origin $P_{500}$ (see grey
shaded regions of figure \ref{fig:Kalannie-CWI-NAB-1Dmarginals})}
\label{tab:Kalannie-InversionRes}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{c|cc|c|c}
\hline
parameter & $E[\bar{X}_i]$ &  $var(\bar{X}_i)$  & $\hat{x}_i^*$ & $P_{500}$\\
\hline
$\hat{x}_2$ & 348 & 220 & 329 & 0.76 \\
\hline
$\hat{x}_3$ & 156 & 433 & 307 & 0.68\\
$\hat{y}_3$ & 369 & 223 & 377 & 0.73\\
\hline
$\hat{x}_4$ & 102 & 402 & -124 & 0.76\\
$\hat{y}_4$ & 58 & 390 & 235 & 0.79\\
$\hat{z}_4$ & 315 & 224 & 201 & 0.81\\
\hline
\end{tabular}
\renewcommand{\arraystretch}{1}
\end{table}

\begin{table}
\caption{Separation estimates between Kalannie event pairs using
the optimisation and Markov-chain Monte-Carlo (MCMC) inversion
results. The separations are generally smaller
than the anticipated rupture size of each event (see table \ref{tab:Kalannie-eventsizes}) suggesting that
the events could rupture overlapping sections of the same fault. We have
more confidence in these separations than the pairwise CWI estimates because they
simultaneously incorporate all coda wave data.}
\label{tab:-KalannieRes-separations}
\begin{tabular}{c|cc}
\hline
Pair & Optimiser & MCMC \\
\hline
$\delta_{12}$ & 329 & 348 \\
$\delta_{13}$ & 486 & 401 \\
$\delta_{14}$ & 333 & 336 \\
$\delta_{23}$ & 378 & 416 \\
$\delta_{24}$ & 548 & 404 \\
$\delta_{34}$ & 496 & 446 \\
\hline
\end{tabular}
\end{table}
